Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-06 workflow/workflow.Rmd
small changes to text

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
if(packageVersion("zinbwave")<"0.99.6") stop("must have current devel version to avoid bugs")
if(packageVersion("clusterExperiment")<"1.3.1.9004") stop("must have current develop version to avoid bugs")
if(packageVersion("scone")<"1.1.2") stop("must have current devel version to avoid bugs")

@@

Note that in order to successfully run the workflow, we need the devel versions
of the Bioconductor packages `scone (>=1.1.2)`, `zinbwave (>=0.99.6)`, and `clusterExperiment (>=1.3.2)` [DR: Elizabeth, please check!]. We recommend running Bioconductor 3.6 (currently the devel version; see https://www.bioconductor.org/developers/how-to/useDevel/).

@@

Finally, to speed up computation, we retain only the 1,000 most variable genes. We recommend, however, not to be so stringent in an actual data analysis.

[FP: add an additional comment to justify that we keep only 1000 most variable genes. We can say that it is enough to recover the signal from [@Fletcher2017]. ]

@@

The distribution of cells across the consensus clusters can be visualized in Figure \@ref(fig:barplotOurs)) and is as follows:

@@

```{r barplotOurs, fig.cap="Barplot of number of cells per cluster, for our workflow's clusterint."}
plotBarplot(ceObj, legend = F) 
```

[FP: Should we add here the short paragraph Elizabeth was talking about to compare our found clusters versus the original published clusters?]
[FP: we should add a comment on cluster 7.]

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
if(packageVersion("zinbwave")<"0.99.6") stop("must have current devel version to avoid bugs")
if(packageVersion("clusterExperiment")<"1.3.2") stop("must have current develop version to avoid bugs")
if(packageVersion("scone")<"1.1.2") stop("must have current devel version to avoid bugs")

@@

Note that in order to successfully run the workflow, we need the devel versions
of the Bioconductor packages `scone (>=1.1.2)`, `zinbwave (>=0.99.6)`, and `clusterExperiment (>=1.3.2)`. We recommend running Bioconductor 3.6 (currently the devel version; see https://www.bioconductor.org/developers/how-to/useDevel/).

@@

Finally, we retain only the 1,000 most variable genes. It speeds up the computations and allows to remove genes with low biological signal. As the 1,000 most variable genes allow to recover the biological signal found in the published analysis ([@Fletcher2017]), we think it is a reasonable choice for this particular analysis. We recommend, however, to explore the number of genes required to extract the biological signal in an actual data analysis.

[FP: check]

@@

The distribution of cells across the consensus clusters can be visualized in Figure \@ref(fig:barplotOurs) and is as follows:

@@

```{r barplotOurs, fig.cap="Barplot of number of cells per cluster, for our workflow's clustering."}
plotBarplot(ceObj, legend = F) 
```

The distribution of cells in our workflow's clustering is in agreement with the distribution of cells in the original published clustering (Figures \@ref(fig:addPublishedClusters) and \@ref(fig:comparePublished)) where the major difference is that in the published analysis several clusters have been merged into single clusters in our workflow's clustering. This difference is likelihood to be caused by the fact that we performed the dimensionality reduction step using the ZINB-WaVE model and input the W matrix to the RSEC function instead of performing the dimensionality reduction on the normalized counts within the RSEC function, resulting

[FP: check]
